\DTLgidxSetDefaultDB{glossary}


\newterm[%
    description={An electric current that periodically reverses direction and is used in most power distribution systems.},
    short={AC},
    long={Alternating Current},
    plural={}
]{AC}

\newterm[%
    description={A semiconductor light source that emits light when current flows through it.},
    short={LED},
    long={Light Emitting Diode},
    plural={LEDs}
]{LED}

\newterm[%
    description={A user interface that allows users to interact with electronic devices through graphical icons and visual indicators.},
    short={GUI},
    long={Graphical User Interface},
    plural={GUIs}
]{GUI}

\newterm[%
    description={The space where interactions between humans and machines occur.},
    short={UI},
    long={User Interface},
    plural={UIs}
]{UI}

\newterm[%
    description={A simple, instance-based learning algorithm that classifies objects based on the closest training examples in the feature space.},
    short={KNN},
    long={k-Nearest Neighbors},
    plural={}
]{KNN}

\newterm[%
    description={An electric current that flows consistently in one direction.},
    short={DC},
    long={Direct Current},
    plural={}
]{DC}

\newterm[%
    description={An optimizer that computes adaptive learning rates for each parameter, combining the advantages of two other extensions of stochastic gradient descent.},
    short={Adam},
    long={Adaptive Moment Estimation},
    plural={}
]{Adam}

\newterm[%
    description={A variant of Adam that decouples the weight decay from the gradient update, which often leads to better generalization and more stable convergence.},
    short={AdamW},
    long={Adam with Decoupled Weight Decay},
    plural={}
]{AdamW}

\newterm[%
    description={The primary component of a computer that performs most of the processing inside a computer, executing instructions from programs.},
    short={CPU},
    long={Central Processing Unit},
    plural={Central Processing Units}
]{CPU}

\newterm[%
    description={A type of deep neural network that is highly effective in analyzing and processing visual data, such as images.},
    short={CNN},
    long={Convolutional Neural Network},
    plural={Convolutional Neural Networks}
]{CNN}

\newterm[%
    description={An object detection system that improves upon R-CNN by using a Region Proposal Network for faster and more efficient detection.},
    short={Faster R-CNN},
    long={Faster Region-based Convolutional Neural Network},
    plural={}
]{Faster R-CNN}

\newterm[%
    description={A series of small single-board computers developed for teaching basic computer science and for DIY electronics projects.},
    short={RPi},
    long={Raspberry Pi},
    plural={Raspberry Pis}
]{RPi}

\newterm[%
    description={A specialized electronic circuit designed to rapidly manipulate and alter memory to accelerate the creation of images, and now widely used for parallel computation in deep learning.},
    short={GPU},
    long={Graphics Processing Unit},
    plural={Graphics Processing Units}
]{GPU}

\newterm[%
    description={A feature of computer systems that allows certain hardware subsystems to access main system memory independently of the central processing unit, significantly speeding up data transfer.},
    short={DMA},
    long={Direct Memory Access},
    plural={}
]{DMA}

\newterm[%
    description={A half-precision floating-point format using 16 bits, commonly used in deep learning to reduce memory usage and computation time.},
    plural={}
]{FP16}

\newterm[%
    description={A 16-bit floating-point format designed for machine learning and AI workloads, offering a different dynamic range trade-off compared to FP16 for improved stability.},
    plural={}
]{BF16}

\newterm[%
    description={The standard single-precision floating-point format using 32 bits, providing a high level of precision for numerical computations.},
    plural={}
]{FP32}

\newterm[%
    description={A learning rate schedule that simulates warm restarts during training, where the learning rate is periodically reset to a high value to help escape local minima.},
    plural={}
]{SGDR}

\newterm[%
    description={The communication between an information processing system and the outside world, often referring to data transfer operations which can be a bottleneck in computing.},
    plural={}
]{I/O}

\newterm[%
    description={A deep neural network architecture that uses skip connections or residual blocks to mitigate the vanishing gradient problem, enabling the training of very deep networks.},
    short={ResNet},
    long={Residual Network},
    plural={}
]{ResNet}

\newterm[%
    description={A convolutional neural network architecture characterized by its simplicity, using multiple stacked 3x3 convolutional layers to increase depth and representational power.},
    short={VGGNet},
    long={Visual Geometry Group Network},
    plural={}
]{VGGNet}

\newterm[%
    description={The darkened black or brown region on the mango's skin resulting from impact, compression, or over-ripening, indicating tissue damage beneath the surface.},
    plural={Bruises}
]{bruises}

\newterm[%
    description={The stage at which a mango has developed its optimal color, texture, flavor, and aroma for consumption.},
    plural={}
]{ripeness}

\newterm[%
    description={A popular variety of mango grown in the Philippines, known for its sweet and juicy flesh.},
    plural={Carabao mangoes}
]{Carabao mango}

% Machine learning performance metrics
\newterm[%
    description={A performance metric that measures the overall proportion of correct predictions made by a machine learning model.},
    plural={}
]{accuracy score}

\newterm[%
    description={A table that summarizes the performance of a classification model, showing the number of true positives, true negatives, false positives, and false negatives.},
    plural={confusion matrices}
]{confusion matrix}

\newterm[%
    description={A balanced performance metric that is the harmonic mean of precision and recall, taking both into account.},
    plural={}
]{F1-Score}

\newterm[%
    description={A subset of Artificial Intelligence that enables systems to learn and improve from data.},
    plural={}
]{machine learning}

\newterm[%
    description={The use of cameras and algorithms to provide imaging-based inspection and analysis.},
    plural={}
]{computer vision}

\newterm[%
    description={A small computing device that controls other parts of a system such as sensors.},
    plural={Microcontrollers}
]{microcontroller}

\newterm[%
    description={A performance metric that reflects the percentage of instances classified as positive that are truly positive.},
    plural={}
]{Precision}

\newterm[%
    description={A performance metric that measures the proportion of actual positive instances that the model correctly identified.},
    plural={}
]{recall}

\newterm[%
    description={A customizable grading system where users can assign weights to grading factors.},
    plural={}
]{User Priority-Based Grading}
