
Show in this chapter proofs why your proposed solution works.  However, presenting results ("It worked") without an appropriate explanation does not show thorough understanding.  Aside from the data and results that you have obtained, and their explanation, the discussion includes why components of your proposed solution work did or did not work in accordance to what you described in the evaluation process, and how the proposed solution performed and faired. Interpret the results and the reasons why they were obtained.  If your results are incorrect, apparent discrepancies from theory should be pointed out and explained. In essence, what do the results mean?  Citing existing publication can help you compare your results and your explanations. 

The next items below is not related to the description of this results and discussions chapter, but serves as an opener for the \LaTeX portion of this template.


In aggregate form, Table~\ref{tab:outcomes_per_objective} shows the outcomes and completions in applying the methodology of the \documentType per objective. \begin{center}
	{\scriptsize
		\begin{tabularx}{\textwidth}{p{0.2\textwidth}|p{0.6\textwidth}|p{0.1\textwidth}}
			\caption{Summary of methods for reaching the objectives} \label{tab:methods_per_objective} \\
			\hline 
			\hline 
			\textbf{Objectives} & 
			\textbf{Methods} & 
			\textbf{Locations} \\ 
			\hline 
			\endfirsthead
			\multicolumn{3}{c}%
			{\textit{Continued from previous page}} \\
			\hline
			\hline 
			\textbf{Objectives} & 
			\textbf{Methods} & 
			\textbf{Locations} \\ 
			\hline 
			\endhead
			\hline 
			\multicolumn{3}{r}{\textit{Continued on next page}} \\ 
			\endfoot
			\hline 
			\endlastfoot
			\hline
			
			\Paste{GO} & 
			\begin{enumerate}
				\item Build an image acquisition system with a conveyor belt, LED lights, and Raspberry Pi Camera
				\item Coded a Raspberry Pi application to grade and sort the Carabao mangoes
			\end{enumerate} 
			& Sec.~\ref{sec:implement} on p.~\pageref{sec:implement} \\ \hline
			
			\Paste{SO1} & \begin{enumerate}
				\item Build a physical prototype 
				\item Developed a Raspberry Pi application to grade and sort the Carabao mangoes
			\end{enumerate} & Sec.~\ref{sec:implement} on p.~\pageref{sec:implement} \\ \hline
			
			\Paste{SO2} & \begin{enumerate}
				\item Trained and tested using a pre-trained CNN model (EfficientNet with Adam optimizer) to classify ripeness and bruises
				\item Classified ripeness into green, yellow-green, and yellow
				\item Classified bruises into bruised and not bruised
			\end{enumerate} & Sec.~\ref{sec:implement} on p.~\pageref{sec:implement} \\ \hline
			
			\Paste{SO3} & \begin{enumerate}
				\item Coded a Raspberry Pi application to control the image acquisition system and conveyor belt
				\item Used a pre-trained CNN model (EfficientNet with Adam optimizer) to classify ripeness and bruises
			\end{enumerate} & Sec.~\ref{sec:implement} on p.~\pageref{sec:implement} \\ \hline
			
			\Paste{SO4} & \begin{enumerate}
				\item Formulated a linear equation based on the inputted user priority and the predicted mango classification
			\end{enumerate} & Sec.~\ref{sec:implement} on p.~\pageref{sec:implement} \\ \hline
			
			\Paste{SO5} & \begin{enumerate}
				\item Used a pre-trained CNN model (EfficientNet with Adam optimizer) to classify ripeness and bruises
				\item Applied computer vision techniques such as foreground mask and thresholding
			\end{enumerate} & Sec.~\ref{sec:implement} on p.~\pageref{sec:implement} \\ \hline
			
		\end{tabularx}
	}
\end{center}



\section{Summary}

Provide the gist of this chapter such that it reflects the contents and the message.